---
title: "psychnet: dependency-free, self-certifying psychometric network estimation in base R"
date: "`r format(Sys.Date())`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    theme: readable
    highlight: tango
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = "")
```

```{r child = "psychnet-clean-room.md"}
```

# Appendix: real-data validation (knitted from the result files)

The tables below are read from the comparison output in `validation/`, generated
by `validation/run_validation.R`. They are not the simulated comparison of
Section 6; they are the agreement with the reference packages on real
questionnaire instruments.

## Part A. EBIC graphical lasso, psychnet vs qgraph, real questionnaire data

```{r}
fa <- file.path("..", "validation", "results_realdata.csv")
if (file.exists(fa)) {
  a <- read.csv(fa, stringsAsFactors = FALSE)
  knitr::kable(a, caption = sprintf(
    "%d instruments. Structure agreement is the zero/nonzero edge-pattern match; max_delta is the largest absolute edge-weight difference.",
    nrow(a)))
} else cat("Run validation/run_validation.R to generate this table.")
```

```{r}
if (file.exists(fa)) {
  a <- read.csv(fa, stringsAsFactors = FALSE)
  cat(sprintf("Across %d instruments the edge set is identical on every one (minimum structure agreement %.3f), and the largest single edge-weight difference is %.5f.\n",
              nrow(a), min(a$struct), max(a$max_delta)))
}
```

## Part B. Ising, psychnet vs IsingFit, real binary data

```{r}
fb <- file.path("..", "validation", "results_ising.csv")
if (file.exists(fb)) knitr::kable(read.csv(fb, stringsAsFactors = FALSE),
  caption = "Binary ability and intelligence items.") else cat("(not generated)")
```

## Part C. Synthetic ground truth: recovery and agreement

```{r}
fc <- file.path("..", "validation", "results_synthetic.csv")
if (file.exists(fc)) knitr::kable(read.csv(fc, stringsAsFactors = FALSE),
  caption = "Data drawn from a known sparse graph. F1 is the edge-recovery F-measure against the truth; struct_vs_qgraph is the psychnet/qgraph agreement.") else cat("(not generated)")
```

---

```{r}
cat(sprintf("Rendered %s with R %s and psychnet %s.",
            format(Sys.time()), getRversion(),
            tryCatch(as.character(packageVersion("psychnet")), error = function(e) "(dev)")))
```
